\documentclass[10pt,a4paper]{scrartcl}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
%\usepackage{setspace}
\usepackage{graphicx}
%\usepackage[export]{adjustbox}
\title{Defence of Olympus Mons Forge}
\subtitle{COMP140 - Proposal}
\author{1700522}
\begin{document}
	\maketitle
	\section{Game}
			The player will be unable to move but will be able to rotate a full 360 degrees. The 	aim of the game is to overcome wave after wave of enemies while defending the forge behind 			the player. If the player can survive 10 waves then the final boss will attack, this boss 			will be mechanically unique compared to the hordes of enemies assaulting the forge but will 		easily have the strength of the entire wave.
	\subsection{Mechanics}
			Within the game the player will be able to rotate left and right, as to face the enemies with the 2 weapons at their disposal. The weapons will be a machine gun and a laser, the machine gun working by firing a number of shots per second the control is held down, the laser on the other hand will function by firing 2 shots in succession then waiting for a recharge before being able to fire again. In addition to these as an extension there may be other weapons implemented such as an explosive cannon that can fire a single explosive shot but will take a long time to recharge. In addition the player will also be able to activate a shield, this will protect them from all damage for a short amount of time but has a long recharge.
			
			The enemies will function as slow moving but heavily armoured targets that will take only a single laser shot to defeat but will take concentrated fire from the machine gun. The enemies will have a shorter range than the player and will fire``Gauss'' weapons that function similarly to the laser but at a weaker power and faster rate.
			
			The boss will function completely differently to the mobs, it will have much more health and 3 abilities; the first is similar to the machine gun as fires an array of weak fast paced shots at the player. The second of these is a focussed beam with a prior charge that will act more like the players laser. The final ability is that the boss can resurrect 3 fallen enemies that will fight for it, this ability will have a long cool down as it would be very difficult for the player to defeat both the boss and a wave of enemies.
	\section{Controller}
			The design of the controller is based around the 2 arm mounted weapons and the rotation of the player character. The 2 weapons will be built into gauntlets with attatched braces, the right hand having a motor for vibration and a simple button trigger that the player would need to hold down to charge and shoot the machine gun while the motor vibrates for tactile feedback. The left hand would have a two stage trigger, the first stage drawing a targeting line and the second shooting the laser cannon, there would be 2 large vibrations from this shot from the motor on the left weapon conroller to simulate the 2 shots. The player will rotate by the use of a single potentiomiter based in a foot pedal turning left or right respectively.
\end{document}